---
title: "Gambeling Analysis Manual"
author: "Dimitri Kestenbaum, Nixia Sancy, and Inder Rana"
date: "12/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library('ggplot2')
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis Overview

The purpose of this manual is to provide our marketing analysis team with a high-level overview of the relevant statistical summaries of this descriptive analysis project. Provided additionally, are explanations for the different features or variables which we engineered as a team in order to extract additional insight from the dataset, which can be used in future analysis such as segmentation or predictive analytics. 

# Basetable Variable Summary Statistics: 
# Total Bets Stats:
```{r}
## Total bets summary sa
load("~/Desktop/marketing_datamart/gambeling_analysis/base_table.Rdata")
summary(base_table$total_bets)
```
#Total Stakes Stats:

```{r}
## Total bets summary sa
summary(base_table$total_stakes)
```
#Total Wins Stats:
```{r}
## Total bets summary sa
summary(base_table$total_wins)
```
#Total Profit Stats: 
```{r}
## Total bets summary sa
summary(base_table$profit)
```
## Created Metrics:

LOR (Length of Relationship):

Calculated by subtracting registration date (RegDate) from the latest date in the dataset October, 2nd 2005. The unit of this measure is days since registration date. As the histogram below displays, the highest count of in the distribution is found in the interval from 220 days to 225 days. 

```{r}
## Total bets summary sa
histogram_LOR <- ggplot(base_table, aes(x=LOR)) +
  geom_histogram() 
histogram_LOR
```




