---
title: "Gambeling Analysis Manual"
author: "Dimitri Kestenbaum, Nixia Sancy, and Inder Rana"
date: "12/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis Overview

The purpose of this manual is to provide our marketing analysis team with a high-level overview of the relevant statistical summaries of this descriptive analysis project. Provided additionally, are explanations for the different features or variables which we engineered as a team in order to extract additional insight from the dataset, which can be used in future analysis such as segmentation or predictive analytics. 

# Basetable Variable Summary Statistics: 
# Total Bets Stats:
```{r cars}
load('base_table.Rdata')
## Total bets summary sa
summary(base_table$total_bets)
```
#Total Stakes Stats:

```{r cars}
## Total bets summary sa
summary(base_table$total_stakes)
```
#Total Wins Stats:
```{r cars}
## Total bets summary sa
summary(base_table$total_wins)
```
#Total Profit Stats: 
```{r cars}
## Total bets summary sa
summary(base_table$profit)
```
## Created Metrics 
